Artin Group Presentations Arising from Cluster Algebras

### 2014-09-05 Paper.tex
Labels Fixed

\begin{center}
\begin{tikzpicture}[baseline=-0.5ex]
\label{mutation}

@@

@@

   \end{tikzpicture}
   \label{fig:cycle_types}
\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
\end{figure}

@@

\label{fig:local_three}
\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
\end{figure}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\bullet& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[left]{2}(dl)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\draw[->]
  (dl) to node[above]{2} (ur)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
    \end{tikzpicture}
    \end{enumerate}
\label{fig:first_cycle_types}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
\end{figure}

@@

\label{fig:second_cycle_types}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
\end{figure}

@@

\begin{def}\cite[Definition 4.1]{FT13}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(R3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{def}

@@

\begin{table}[h] \label{table1}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (R4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$ \\ \hline
\end{tabular}
\caption{(R4) Relations}
\end{table}

@@

\begin{defn}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $A_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(T2)] $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(T3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table2}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{defn}

@@

\begin{table}[h] \label{table2}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (T4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $s_{2}s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1} = s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$ \\ \hline
\end{tabular}
\caption{(T4) Relations}
\end{table}

>>>>

\begin{figure}
\begin{center}
\begin{tikzpicture}[baseline=-0.5ex]

@@

\caption{Mutation of $\Gamma$ at a node k}\label{mutation}
\end{figure}

@@

\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}} \label{fig:cycle_types}
\end{figure}

@@

\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}} \label{fig:local_three}
\end{figure}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\bullet& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[left]{2}(dl)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\draw[->]
  (dl) to node[above]{2} (ur)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
    \end{tikzpicture}
    \end{enumerate}

\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}} \label{fig:first_cycle_types}
\end{figure}

@@

\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}} \label{fig:second_cycle_types}
\end{figure}

@@

\begin{def}\cite[Definition 4.1]{FT13}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(R3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table1}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{def}

@@

\begin{table}[h] 
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (R4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$ \\ \hline
\end{tabular}
\caption{(R4) Relations} \label{table1}
\end{table}

@@

\begin{defn}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $A_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(T2)] $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(T3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table2}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{defn}

@@

\begin{table}[h] 
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (T4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline

@@

\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $s_{2}s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1} = s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$ \\ \hline
\end{tabular}
\caption{(T4) Relations} \label{table2}
\end{table}
